Noisy Work: A Review of The Uncertainty Visualisation Literature

### 2024-02-27 paper.qmd
formatting changes to paper

**Aside:this is all currently from the spieglehatter paper because that is the only paper I have moved notes over from mendeley before I started doing the summary write up. this will not all be from one paper, dont worry.**

**Aside:This section still needs some citations from papers that communicate uncertainty, but the are *hard* to organise because of the ambiguous uncertainty definition problem. So they will all be communicating something different but you cant find out what it is until you are knee deep in the method section.**

@@

Computational equivalency in visualisation is also something that has been well researched. For simple tasks such as value extraction, there is a hierarchy to perceptual tasks where extracting visual information in some forms is easier than others. The hierarchy established 40 years ago by @Cleveland1984 is:  
1) position along a common scale. 
2) position along a non-aligned scale. 
3) length. 
4) angle/slope. 
5) area. 
6) volume. 
7) colour

>>>>

> Edit note: Currently these notes are just from spiegelhater because this is the only paper I have moved notes over from. Other sources will be used here lol. Working out what exactly they are communicating is a bit of a pain though.

@@

Computational equivalency in visualisation is also something that has been well researched. For simple tasks such as value extraction, there is a hierarchy to perceptual tasks where extracting visual information in some forms is easier than others. The hierarchy established 40 years ago by @Cleveland1984 is:

1) position along a common scale. 
2) position along a non-aligned scale. 
3) length. 
4) angle/slope. 
5) area. 
6) volume. 
7) colour
